---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}

set.seed(1982)
pacman::p_load(R2jags, polspline, tidyverse)

```

```{r}

groupSize <- 4
ntrials <- 10
pi <- 1.4
ntokens <- 20
vals <- seq(1,21,1) #possible values to contribute - from 0 to 20 tokens
vals
```

```{r}

d <- read.csv("HerrmannThoeniGaechterDATA.csv", skip = 3) # Public goods game

```

```{r}

# create variable for GINI. Data from 
# http://hdr.undp.org/sites/default/files/reports/269/hdr_2009_en_complete.pdf,

d <- d %>% 
  mutate(gini = case_when(
    city == "Melbourne" ~ 34.3,
    city == "Minsk" ~ 25.3,
    city == "Chengdu" ~ 38.5,
    city == "Copenhagen" ~ 28.7,
    city == "Bonn" ~ 31.9,
    city == "Athens" ~ 34.4,
    city == "Seoul" ~ 31.6,
    city == "Samara" ~ 37.5,
    city == "Zurich" ~ 32.7,
    city == "St. Gallen" ~ 32.7,
    city == "Istanbul" ~ 41.9,
    city == "Nottingham" ~ 34.8,
    city == "Dnipropetrovs'k" ~ 26.1,
    city == "Boston" ~ 41.1
  ))


```

```{r}

# extract every third line - data file has lines representing others responses and we don't need that
d1 <- d[seq(1,length(d$sessionid),3),]

group_names <- unique(d1$groupid)
ngroups <- length(group_names)

# THIS WILL REMOVE SUBJECTS WITH MISSING DATA IN NO PUNISHMENT CONDITION
ngroups <- 269

subject_names <- unique(d1$subjectid)
nsubjects <- length(subject_names)

```

```{r}
# data for no punishment condition #
c_no_punish <- array(0,c(groupSize,ntrials,ngroups))
Ga_no_punish <- array(0,c(ntrials,ngroups))
Gc_no_punish <- array(0,c(groupSize,ntrials,ngroups))
Gc_four <- array(0, c(groupSize, ntrials, ngroups))
missing <- array(0,ngroups)

```

```{r}

# your loop (Gc_no_punish)
for (g in 1:ngroups) {
  c_no_punish[,,g] <- rbind(d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][1:10],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][11:20],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][21:30],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][31:40])
  
  Ga_no_punish[,g] <- colMeans(c_no_punish[,,g])
  
  missing[g] <- is.na(c_no_punish[1,1,g])
  
  for (s in 1:groupSize) {
    Gc_no_punish[,,g] <- colSums(c_no_punish[-s,,g])
  }
}

## are they the same?
all.equal(Gc_no_punish, Gc_four)


# array with same dimensions as Gc_no_punish
Gc_four <- array(0, c(groupSize, ntrials, ngroups))

# hard-coding s to 4. 
# shows that your for-loop just overwrites. 
# does not make a lot of sense. 
for (g in 1:ngroups) {
  c_no_punish[,,g] <- rbind(d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][1:10],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][11:20],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][21:30],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][31:40])
  
  Ga_no_punish[,g] <- colMeans(c_no_punish[,,g])
  
  missing[g] <- is.na(c_no_punish[1,1,g])
  
  # we changed stuff here. 
  # no for-loop, just the last groupsize. 
  Gc_four[,,g] <- colSums(c_no_punish[-4,,g])

}

# are they the same?: yes. 
# is this really the intended functionality? 
all.equal(Gc_no_punish, Gc_four)
 
```

```{r}
# data for punishment condition #
c_punish <- array(0,c(groupSize,ntrials,ngroups))
Ga_punish <- array(0,c(ntrials,ngroups))
Gc_punish <- array(0,c(groupSize,ntrials,ngroups))

```


```{r}

for (g in 1:ngroups) {
  c_punish[,,g] <- rbind(d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="P-experiment"][1:10],
                         d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="P-experiment"][11:20],
                         d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="P-experiment"][21:30],
                         d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="P-experiment"][31:40])
  
  Ga_punish[,g] <- colMeans(c_punish[,,g])
  
  for (s in 1:groupSize) {
    Gc_punish[,,g] <- colSums(c_punish[-s,,g])
  }
}

```

```{r}
# compile data from each condition into 4D matrix
c <- array(0,c(groupSize,ntrials,ngroups,2))
c[,,,1] <- c_no_punish
c[,,,2] <- c_punish

Ga <- array(0,c(ntrials,ngroups,2))
Ga[,,1] <- Ga_no_punish
Ga[,,2] <- Ga_punish

Gc <- array(0,c(groupSize,ntrials,ngroups,2))
Gc[,,,1] <- Gc_no_punish
Gc[,,,2] <- Gc_punish

c_choice_index <- c

Gini <- array(0,c(ngroups))
for (g in 1:ngroups) {
  Gini[g] <- mean(d1$gini[d1$groupid==group_names[g]&d1$p=="P-experiment"])
}

Ga_punish <- Ga_punish[,!is.na(Gini)]
Ga_no_punish <- Ga_no_punish[,!is.na(Gini)]

c <- c[,,!is.na(Gini),]
Ga <- Ga[,!is.na(Gini),]
Gc <- Gc[,,!is.na(Gini),]
Gini <- Gini[!is.na(Gini)]

#redefine number of groups after removing those without civic scores
ngroups <- length(Gini)


```

Apply decay model to data

```{r}
data <- list("ntrials","ngroups","groupSize","Gini","c") #data inputted into jags
params <- c("c0","gamma","beta0_c0","betaGini_c0","beta0_gamma","betaGini_gamma")

```

```{r}
# - run jags code
decay.samples <- jags(data, inits=NULL, params,
                      model.file ="decay.txt",
                      n.chains=1, n.iter=2000, n.burnin=1000, n.thin=1)

```

```{r}
# Bayes factors and credible intervals for effect of Gini on initial contribution
prior <- dnorm(0,1)
fit.posterior <- logspline(decay.samples$BUGSoutput$sims.list$betaGini_c0)
posterior <- dlogspline(0, fit.posterior) # this gives the pdf at point delta = 0
decay.betaGini_c0.BF <- prior/posterior

decay.betaGini_c0.CIL <- qlogspline(0.025,fit.posterior) #2.5% CI
decay.betaGini_c0.CIH <- qlogspline(0.975,fit.posterior) #97.5% CI

```

```{r}
# Bayes factors and credible intervals for effect of Gini on decay in contribution
prior <- dnorm(0,1)
fit.posterior <- logspline(decay.samples$BUGSoutput$sims.list$betaGini_gamma)
posterior <- dlogspline(0, fit.posterior) # this gives the pdf at point = 0
decay.betaGini_gamma.BF <- prior/posterior

decay.betaGini_gamma.CIL <- qlogspline(0.025,fit.posterior) #2.5% CI
decay.betaGini_gamma.CIH <- qlogspline(0.975,fit.posterior) #97.5% CI

```

Apply CC model to data 

```{r}
#standardise Gini score for analysis - we need to do this because model is more complex and won't converge otherwise
Gini_unst <- Gini #used for plotting unstandardised
Gini <- (Gini-mean(Gini))/sd(Gini)

data <- list("groupSize", "ngroups", "ntrials", "ntokens","vals","c","Ga","Gini") #data inputted into jags
params <- c("beta0_pbeta","betaGini_pbeta",
            "mu_pbeta_probit") #parameters we'll track in jags

```

```{r}
# - run jags code
CC.samples <- jags(data, inits=NULL, params,
                   model.file ="CC_Gini.txt",
                   n.chains=1, n.iter=2000, n.burnin=1000, n.thin=1)

prior <- dnorm(0,1)
fit.posterior <- logspline(CC.samples$BUGSoutput$sims.list$beta0)
posterior <- dlogspline(0, fit.posterior) # this gives the pdf at point delta = 0
CC.beta0.BF <- prior/posterior

CC.betaGini.CIL <- qlogspline(0.025,fit.posterior) #2.5% CI
CC.betaGini.CIH <- qlogspline(0.975,fit.posterior) #97.5% CI

```

```{r}

bmp(file="decay_plot.bmp",
    width=13, height=13, units="in", res=100)

layout(rbind(c(1,1,3,3,4,4), 
             c(1,1,3,3,5,5),
             c(2,2,6,6,7,7), 
             c(2,2,6,6,8,8)))

par(cex=1.1)

```

### DECAY 

model {
  
  beta0_c0 ~ dnorm(0,1)T(0,) 
  betaGini_c0 ~ dnorm(0,1)

  beta0_gamma ~ dnorm(0,1)T(0,) 
  betaGini_gamma ~ dnorm(0,1)

  for (g in 1:ngroups) {
  
    for (s in 1:groupSize) {

      sigma_c[s,g] ~ dgamma(1,1)

      ################### Linear model for initial contrib  ###################
      c0[s,g] <- beta0_c0 + (betaGini_c0*Gini[g])

      ################### Linear model for decay  ###########################
      gamma[s,g] <- beta0_gamma + (betaGini_gamma*Gini[g])

      ##################  Individual Decay model  ############################
      for (t in 1:ntrials) {
  
        mu_c[s,t,g] <- c0[s,g]*exp(-gamma[s,g]*t)
        c[s,t,g,1] ~ dnorm(mu_c[s,t,g],sigma_c[s,g])

        
      }
    }
    
  }  
    
}

```{r}
for (t in 2:10){
  print(t)
}
```


### CC 
model {

  #data is nagents, ntrials, index of vals, matrix of contributions (c), and average contribution (Ga)
  
  beta0_pbeta ~ dnorm(0,1) 
  betaGini_pbeta ~ dnorm(0,1)
  
  #######################################################################################################
  
  for (g in 1:ngroups) {
  
    for (s in 1:groupSize) {
    
      #--------------------------------------------------------------------------------------------------
      #------------------------- Individual regression priors -------------------------------------------
      #--------------------------------------------------------------------------------------------------
      
      mu_pbeta_probit[s,g] <- beta0_pbeta + (betaGini_pbeta*(Gini[g]))
      
      sigma_pbeta[s,g] ~ dunif(1,100) #concentration parameter for reparameterised beta distribution
      
      # reparameterising beta prior for slope of beliefs/preferences  in CC model 
      probit(mu_pbeta[s,g]) <- mu_pbeta_probit[s,g] # probit descale - - mean for cond is lower than overall
      shape1_pbeta[s,g] <- (mu_pbeta[s,g]) * sigma_pbeta[s,g]
      shape2_pbeta[s,g] <- (1 - mu_pbeta[s,g]) * sigma_pbeta[s,g]  

      #---------------------------------------------------------------------------------------------------
      #------------------------- Model level priors ------------------------------------------------------
      #---------------------------------------------------------------------------------------------------
      #initial weighting of beliefs about others contributions in choice of own contribution, relative to prefs
      omega1[s,g] ~ dbeta(1,1) 
        
      #decay rate in weighting of beliefs about others - prefs dominate over time
      lambda[s,g] ~ dbeta(1,1)
        
      #parameter weighting of beliefs about what others will contribute, relative to observed contribution
      gamma[s,g] ~ dbeta(1,1)
        
      #~ dunif(0,20) #intercept of linear model relating preferred contributions to possible contribution values
      p0[s,g] <- 0

      #slope of linear model relating preferred contributions to possible contribution values
      pbeta[s,g] ~ dbeta(shape1_pbeta[s,g]+1,shape2_pbeta[s,g]+1)
        
      for (i in 1:length(vals)) {
        #vector of preferred contributions for each possible value - linear relationship
        pvals[s,i,g] <- p0[s,g] + (pbeta[s,g]*vals[i]) 
      }
        
      omega[s,1,g] <- omega1[s,g]
        
      #assume beliefs about others on first trial is reflected in first contribution. Simplification for model.
      Gb[s,1,g] <- c[s,1,g,1] 
        
      mu_c[s,1,g] <- Ga[1,g,1]
    }


    for (t in 2:ntrials) {
        
      for (s in 1:groupSize) {
        
        Gb[s,t,g] <- (gamma[s,g]*(Gb[s,t-1,g]))+((1-gamma[s,g])*(Ga[t-1,g,1]))
          
        #this line is necessary to avoid zero indexing
        pval_index[s,t,g] <- ifelse(round(Gb[s,t,g])>1,round(Gb[s,t,g]),1)
          
        p[s,t,g] <- pvals[s,pval_index[s,t,g],g]
          
        omega[s,t,g] <- omega[s,t-1,g]*(1-lambda[s,g])
          
        # departs from simulation function. Data needs to be stochastic,
        # so we don't simulate c directly, rather mean of c distribution
        mu_c[s,t,g] <- ((omega[s,t,g])*Gb[s,t,g]) + ((1-omega[s,t,g])*p[s,t,g]) 
          
        c[s,t,g,1] ~ dnorm(mu_c[s,t,g],.1)
      }
        
    }
  }
  
}
