---
title: "Untitled"
output: html_document
---

## same as yours

```{r setup, include=FALSE}

set.seed(1982)
pacman::p_load(R2jags, polspline, tidyverse)

```

## same as yours 

```{r}

groupSize <- 4
ntrials <- 10
pi <- 1.4
ntokens <- 20
vals <- seq(1,21,1) #possible values to contribute - from 0 to 20 tokens

```

## same as yours

```{r}

d <- read.csv("HerrmannThoeniGaechterDATA.csv", skip = 3) # Public goods game

```

## does the same as yours

```{r}

# create variable for GINI. Data from 
# http://hdr.undp.org/sites/default/files/reports/269/hdr_2009_en_complete.pdf,

d <- d %>% 
  mutate(gini = case_when(
    city == "Melbourne" ~ 34.3,
    city == "Minsk" ~ 25.3,
    city == "Chengdu" ~ 38.5,
    city == "Copenhagen" ~ 28.7,
    city == "Bonn" ~ 31.9,
    city == "Athens" ~ 34.4,
    city == "Seoul" ~ 31.6,
    city == "Samara" ~ 37.5,
    city == "Zurich" ~ 32.7,
    city == "St. Gallen" ~ 32.7,
    city == "Istanbul" ~ 41.9,
    city == "Nottingham" ~ 34.8,
    city == "Dnipropetrovs'k" ~ 26.1,
    city == "Boston" ~ 41.1
  ))


```

## same as yours

```{r}

# extract every third line - data file has lines representing others responses and we don't need that
d1 <- d[seq(1,length(d$sessionid),3),]

group_names <- unique(d1$groupid)
ngroups <- length(group_names)

# THIS WILL REMOVE SUBJECTS WITH MISSING DATA IN NO PUNISHMENT CONDITION
ngroups <- 269

subject_names <- unique(d1$subjectid)
nsubjects <- length(subject_names)

```

## Same as yours

```{r}
# data for no punishment condition #
c_no_punish <- array(0,c(groupSize,ntrials,ngroups))
Ga_no_punish <- array(0,c(ntrials,ngroups))
Gc_no_punish <- array(0,c(groupSize,ntrials,ngroups))
missing <- array(0,ngroups)

```

## Same as yours

```{r}

# your loop (Gc_no_punish)
for (g in 1:ngroups) {
  c_no_punish[,,g] <- rbind(d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][1:10],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][11:20],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][21:30],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][31:40])
  
  Ga_no_punish[,g] <- colMeans(c_no_punish[,,g])
  
  missing[g] <- is.na(c_no_punish[1,1,g])
  
  for (s in 1:groupSize) {
    Gc_no_punish[,,g] <- colSums(c_no_punish[-s,,g])
  }
}


```

## The point. 
Here we come to it. 
So, we could not make sense of the output of Gc_no_punish.
This code showcases our confusion.
We have omitted the for-loop over groupSize,
and just hard-coded it to the last group, which is 4
(i.e. we are not looping over groupSize with "s"). 
This gives the same result as your code - i.e.
all.equals(Gc_no_punish, Gc_four) is TRUE. 
How does this make sense?
I.e. your for-loop does not update the value in 
Gc_no_punish, but just overwrites it. 
This surely cannot be the intended functionality?

Furthermore, we cannot tell when you actually use 
Gc_no_punish (or Gc_punish) in the models? 
I.e. it seems that you just create them and then
don't use them..? We checked in the model specifications
(the .txt files) and no "Gc" is used there either. 

```{r}

# array with same dimensions as Gc_no_punish
Gc_four <- array(0, c(groupSize, ntrials, ngroups))

# hard-coding s to 4. 
# shows that your for-loop just overwrites. 
# does not make a lot of sense. 
for (g in 1:ngroups) {
  c_no_punish[,,g] <- rbind(d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][1:10],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][11:20],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][21:30],
                            d1$senderscontribution[d1$groupid==group_names[g]&d1$p=="N-experiment"][31:40])
  
  Ga_no_punish[,g] <- colMeans(c_no_punish[,,g])
  
  missing[g] <- is.na(c_no_punish[1,1,g])
  
  # we changed stuff here. 
  # no for-loop, just the last groupsize. 
  Gc_four[,,g] <- colSums(c_no_punish[-4,,g])

}

# are they the same?: yes. 
# is this really the intended functionality? 
all.equal(Gc_no_punish, Gc_four)
 
```
